Composing Robustly Safe Compilers

### 2023-06-11 popl/main.tex
Add overview for monitor section.

>>>>

This subsection presents monitors for our properties of interest (\gls{tms}, \gls{sms}, \gls{ms}, \gls{scct}).
Each monitor has its own accompanying trace model that abstracts over our most general trace model.
This is because monitors should only be concerned with property-relevant information.
For each such monitor-specific trace model, we define an agreement relation that relates it with the most general trace model.
Lastly, if any monitor does not get stuck on a trace and the trace agrees with a most general trace, then the most general one satisfies the associated property of the monitor.

\paragraph{\glsfirst{tms}}
\paragraph{\glsfirst{sms}}
\paragraph{\glsfirst{ms}}
\paragraph{\glsfirst{scct}}
